Local Normalisation using the Empirical Null for Inspection of Additive Manufacturing using X-Rays

### 2019-04-28 reports/paper1/paper.tex
Revision

\begin{abstract}
X-ray computed tomography (CT) can be used for defect detection in additive manufacturing. The object is scanned at multiple angles to reconstruct the object in 3D space. The process can be time consuming. The aim is to investigate if it is possible to conduct defect detection from a single scan to speed up the quality control procedure. An experiment was conducted, a 3D printed sample was manufactured with voids to see if they can be detected.

Software, \texttt{aRTist}, was used to simulate the scan and it was compared with the x-ray acquisition under the face of uncertainty. Each pixel was treated as a hypothesis test. The software, and the information provided to it, was not perfect which led to model misspecification and incorrect inference. The empirical null filter was proposed. It locally normalise each test statistic using robust estimators of the mean and deviation. This reduces the number of false positives. Sensible inference was achieved in the simulation and experiment.
\end{abstract}

@@

Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves calculations on acquisition of hundreds of angles of the sample.

Speeding up the quality control process on the production line could be done by doing inspection on a few number of x-ray images \citep{warnett2016towards}. These x-ray images are compared with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods.

A method was proposed to compare the x-ray image with \texttt{aRTist} by treating the simulation of \texttt{aRTist} as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of \texttt{aRTist} do not match up perfectly with the x-ray image, producing incorrect inference. The empirical null filter is demonstrated on simulated and real data.

\section{Method}

@@

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD of a 3D cuboid with voids; the scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

@@

The 3D printed sample was scanned 20 times. The 20 x-ray images were spilt into 2. 19 random images were held out. The remaining image was used to compare with \texttt{aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.

@@

\section{Simulation}

@@

Contamination is the result of a linear transform of the test statistics $Z_{x,y}$. For example in this experiment, the image was multiplied by 2 and a gradient was added to it. Suppose the image does contain defects, then an example of a resulting distribution is
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
\end{align}
where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this experiment to simulate a contaminated image with defects. The contaminated square defected image is shown in Figure \ref{fig:inference_defectSquare2Example}.

@@

An experiment was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$. Hypothesis testing was done on the uncontaminated and filtered contaminated image. The area under the ROC curve and various errors were recorded. This was repeated 100 times by simulating another contaminated image with a defect. To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination. The results are shown in Figure \ref{fig:inference_Experiment_DefectRadiusSquare}.

@@

The results showed that the ROC area increased with kernel radius. This highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination. It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.

@@

The empirical null was used on the real data. The x-ray image was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the 3D printed object. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}.

>>>>

\begin{abstract}
X-ray computed tomography can be used for defect detection in additive manufacturing. The object is scanned at multiple angles to reconstruct the object in 3D space. To avoid this time consuming process, it was investigated whenever it is possible to detect defects based on a single scan. A 3D printed sample was manufactured with voids to see if they can be detected. The x-ray acquisition was compared with a simulation of that scan under the face of uncertainty by treating each pixel as a hypothesis test. The empirical null filter locally normalises each test statistic using robust estimators of the mean and deviation so that sensible inference was achieved.
\end{abstract}

@@

Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves calculations on the acquisition of hundreds of angles of the sample.

Speeding up the quality control process on the production line could be done by doing an inspection on a few numbers of x-ray images \citep{warnett2016towards}. These x-ray images are compared with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods.

A method was proposed to compare the x-ray image with \texttt{aRTist} by treating the simulation of \texttt{aRTist} as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. However beforehand, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of \texttt{aRTist} do not match up perfectly with the x-ray image, producing incorrect inference.

An x-ray image of a 3D printed sample was obtained and compared with the \texttt{aRTist} simulation in an experiment. The procedure is shown in the methods section along with the description of the empirical null filter. In addition, the software development and simulation studies of the filter was discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

\section{Methods}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
  \caption{CAD of a 3D cuboid with voids. The voids were of various diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

@@

The 3D printed sample was scanned 20 times at a fixed angle. The 20 x-ray images were spilt into 2. 19 random images were held out. The remaining image was used to compare with \texttt{aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.

@@

\subsection{Simulation}

@@

Contamination is the result of a linear transform of the test statistics $Z_{x,y}$. For example in this experiment, the image was multiplied by 2 and a gradient was added to it. Suppose the image does contain defects, then an example of a resulting distribution is
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
\end{align}
where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this study to simulate a contaminated image with defects. The contaminated square defected image is shown in Figure \ref{fig:inference_defectSquare2Example}.

@@

A simulation study was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$. Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image. The area under the ROC curve and various errors were recorded. This was repeated 100 times by simulating another image. To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.

@@

The result from the simulation is shown Figure \ref{fig:inference_Experiment_DefectRadiusSquare}. The ROC area increased with kernel radius which highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination. It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.

@@

In the experiment with the 3D printed sample, the x-ray image was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the 3D printed object. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}.
